Discrete Ordinates

### 2017-05-01 docprep/chapmeth.tex
Added more description of the AMPX format

DOCTORS reads AMPX fromatted binary data files. Figure~\ref{fig:ampx} shows the data format of the overall file.

@@

The next block of data contains the average cros section data.

@@

\begin{figure}[tb]
  \begin{center}
   \includegraphics[width=3.75in]{figs/spatial_disc}
  \end{center}
  \caption{The spatial mesh imposed on the problem domain.}
\label{fig:spatial_disc}
\end{figure}%

>>>>

The file is split into a series of records. Each record is a string of binary bytes between a four byte header and four byte footer. The header and footer are identical and, when interpreted as a signed four byte integer, give the size in words of the record. A word is a 32-bit chunk (4 bytes) of binary data. The data is stored in Big Endian format which must be converted to Little Endian for most Intel and AMD processors. An example record is shown in Fig.~\ref{fig:ampxbytes1} and the endianess rearrangement is shown in Fig.~\ref{fig:ampxbytes2}. Once the bytes are properly ordered, the entire string can be reinterpreted as a 32-bit integer. In the case of the header bytes given in Fig.~\ref{fig:ampxbytes1} and~\ref{fig:ampxbytes2}, the bytes correspond to the integer 440 which is the length in bytes of the header record.

\begin{figure}[tb]
  \begin{center}
   \includegraphics[width=3.75in]{figs/ampxbytes1}
  \end{center}
  \caption{The bytes}
\label{fig:ampxbytes1}
\end{figure}

\begin{figure}[tb]
  \begin{center}
   \includegraphics[width=3.75in]{figs/ampxbytes2}
  \end{center}
  \caption{The byte ordering.}
\label{fig:ampxbytes2}
\end{figure}

The size always reports the number of 32-bit words required to store the data. However, some data types, such as characters, are only 8 bits so each word represents four distinct characters.

DOCTORS reads AMPX fromatted binary data files. Figure~\ref{fig:ampx} shows the data format of the overall file. The header section contains information about each individual nuclide such as which reaction types are available as well as information the same such as the group structure information.

The first entry in a nuclide is the directory record. The directory contains general information regarding the nuclide and information necessary to parse the proceeding records.

@@

The next block of data contains the average cross section data. This data is averaged over all energies and directions using Eq.~\ref{eq:groupxs}. The only data used in this section in DOCTORS is the total cross section values necessary for implementing the fully discretized form of the LBE given later.

@@

\begin{figure}[tb]
  \begin{center}
   \includegraphics[width=3.75in]{figs/spatial_disc}
  \end{center}
  \caption{The spatial mesh imposed on the problem domain.}
\label{fig:spatial_disc}
\end{figure}
